JSSET: JavaScript Syntax and Semantics Extraction Toolchain

### 2019-08-16 icse/framework.tex
fix section 5.2 and 7

In this section, we will demonstrate how our idea can be implemented to evaluate programming language. Although it is hard to generalize the process because the format of specification or 
environment of the programming language is varying, We shows the possibility to build entire system for evaluating target language with minimal human effort by giving end-to-end example of ECMAScript language.

@@

\subsection{Generating initial environment for evaluating}
For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsic objects. We will describe how to generate each component.

@@

 Builtin object is pre-defined object with many built-in functions. For example, In ECMAScript \( \code{Array} \) refers an object which can generate an array by
 calling it. Each Builtin Object provides fields and function, just as ordinary object. When its function is called,
 the corresponding algorithm specified in the document should be called.

 In specification, a built-in function object usually matches to abstract algorithm. Its algorithm name
 describes the hierarchy about object it should be contained. For example, there is an abstract algorithm named \( \code{ Object.prototype.propertyIsEnumerable } \). With its name,
 we can know that it corresponds to builtin function in the object \( \code{ Object.prototype } \) as attribute. 
 To support builtin object, we make structure of builtin object and its attributes.
 After we correctly organizes structure, then we made algorithm that automatically map corresponding field to the abstract algorithm in specification by matching its function name.

@@

 While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently referred in specification. But name of builtin objects
 are defined for reference in Host language, so it needs another name to refer it in specification language. For example, \( \code{Array} \) is a name for
 ECMAScript reference, so abstract algorithm should call \\
 \( \code{realm.[[GlobalObject]].[[GetOwnProperty]]("Array")} \) to get ECMAScript \( \code{Array} \) object. Instead of this verbose way, abstract algorithm introduces Intrinsic objects, which
are alias for built-in objects. For example it is referred as \( \code{\%Array\%} \) to refer Array Object.
 Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.

@@

In this case, algorithm dispatching should consider receiver Object(i.e. \( \code{x.[[GetOwnProperty]](N)} \)).
For method-like abstract operation, we organized map from algorithm name to function for each type,
 and we insert functions as property of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
 then we insert attributes with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.

>>>>

In this section, we demonstrate how our idea can be implemented for target language. Although it is hard to generalize the process because the format of specification or
environment of the programming language is varying, We shows the possibility to build entire system to extract target language specification and interpreting it with minimal human effort by giving end-to-end example of ECMAScript language.

@@

\subsection{Generating initial environment for execution}
For ECMAScript Specification, initial environment consists of the Builtin objects, and Intrinsic objects. We describe how to generate each component.

@@

 Builtin object is a pre-defined object with many built-in functions. For example, In ECMAScript \( \code{Array} \) corresponds to an object which can generate an array by
 calling it. Each builtin object provides data property and functions, just as ordinary object. When its function is called,
 its algorithm specified in the document should be called.

 In specification, a builtin function object usually matches to abstract algorithm. Its algorithm name
 describes the hierarchy about object it should be contained. For example, there is an abstract algorithm named \( \code{ Object.prototype.propertyIsEnumerable } \). With its name,
 we can know that it corresponds to builtin function in the object \( \code{ Object.prototype } \) as property.
 To support builtin object, we make structure of builtin object and its properties.
 After we correctly organizes structure, then we made algorithm that automatically map corresponding field to the abstract algorithm in specification by matching its function name.

@@

 In specification, "Well-known intrinsics are built-in objects that are explicitly referenced by the algorithms".
 Abstract algorithm uses name like "\%name\%", which are alias for builtin objects. For example it refers builtin Array object as \( \code{\%Array\%} \) .
 Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.

@@

In this case, algorithm dispatching should consider receiver Object(i.e. \( \code{x.[[GetOwnProperty]](N)} \)).
For method-like abstract operation, we organized map from algorithm name to function for each type,
 and we insert functions as property of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
 then we insert property with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.

### 2019-08-16 icse/related.tex
fix section 5.2 and 7

\subsection{Formal Semantics of JavaScript}
Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many researches to define formal semantics of JavaScript and
using it to formal verification or program analysis. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugaring. Their method can
work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,
which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaScript based on ECMAScript specification, and they manually convert from specification
to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verification and analysis. Similarly, JaVerT coverts specification
to their own language (called JSIL) to make further analysis. Compared to these approaches, we suggests to generate converter from specification to intermediate language, with
conversion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.

>>>>

\subsection{Formal Semantics of JavaScript}

% Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
% web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many researches to define formal semantics of JavaScript and
% using it to formal verification or program analysis.
There are also many researches to define formal semantics of JavaScript. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugaring. Their method can
work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,
which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaScript based on ECMAScript specification, and they manually convert from specification
to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verification and analysis. Similarly, JaVerT coverts specification
to their own language (called JSIL) to make further analysis. Compared to these approaches, we suggests to generate converter from specification to intermediate language, with
conversion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.
